\scriptsize
  \begin{tabularx}{\linewidth}{p{0.2\linewidth} X}
    \multicolumn{2}{l}{\textbf{\textsc{Table Legend}}} \\
    \hline\hline

    \textit{italics}      &Parent categories in italics cannot be selected and are displayed for organizational purposes only. Selecting one of the children categories is required. \\
   \underline{underline}        & Underlined fields were added or modified from the original source.\\
    \hline\hline
     \end{tabularx}

\begin{landscape}

\begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{6}{l}{\textbf{Table 2: Controlled Vocabularies}} \\
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Source: \href{https://vocabularies.cessda.eu/vocabulary/TopicClassification?lang=en}{CESSDA})}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1. & Demography & & & & \\
       &            & 1.1 & Census & Demography.Censuses & 
Surveys of an entire population, as opposed to a sample survey. Often used for official enumerations of a population, usually including the collection of related demographic information. Note that in some countries censuses are not used as demographic information can be obtained from official registers.\\
       &            & 1.2 & Migration & Demography.Migration & 
Includes immigration, emigration, internal migration as well as other types of geographical mobility. Immigration means coming to settle in another country than one's home country. Emigration means leaving one's home country to settle in another country. Migration is an umbrella term for both. Migration also includes internal migration, that is, movement of people within one country at different geographical levels. \\
       &            & 1.3 & Morbidity and mortality & \thead{Demography.MorbidityAnd \\ Mortality} & Morbidity refers to incidence of ill health in a population. Data may cover the incidence or morbidity rate of a medical condition. For example, the number of people who suffer from lung cancer in a country or a geographic area during a single year. Mortality data indicate the numbers of deaths in a population by place, time, cause, or type of individual etc. For example, maternal mortality rate, child mortality rate. Use note: Self-reported survey data on illnesses and medical conditions are indexed with HEALTH hierarchy topics.\\
    2. & Economics & & & &\\
       &            & 2.1 & Consumption and \newline consumer behaviour & \thead{Economics.ConsumptionAnd \\ ConsumerBehaviour} & Refers to the act of acquiring and/or using something to meet the needs and wants of a person, community or society. Data in this category include patterns of consumer behaviour, changes in them, and data on consumer ethics. For example, survey data on how often people buy certain items; when and where they shop; whether ethical considerations affect their consumer choices.\\
    \hline
    \end{tabularx}
  

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
            &            & 2.2 &  Economic conditions and indicators & \thead{Economics.EconomicConditionsAnd\\Indicators} & Economic indicators indicate in which direction an economy is headed and include, for example, GDP growth rate, employment, inflation and interest rate, consumer and investor activity, household debt. Use note: This topic is also used for economic conditions of individuals and households which are surveyed or registered. \\ 
       &            & 2.3 & Economic policy, \newline public expenditure and revenue & \thead{Economics.EconomicPolicyPublic \\ ExpenditureAndRevenue} & Data on economic policy, including budget and fiscal policy, public expenditure and public revenue.\\
       &            & 2.4 &  Economic systems and development & \thead{Economics.EconomicSystemsAnd \\Development} &
Data covering capitalist, socialist and other economic systems and data on, for example, international development programs. \\ 
       &            & 2.5 &  Income, property and \newline investment/saving & \thead{Economics.IncomePropertyAnd\\InvestmentSaving} & Data on the accumulation of personal assets, including income, property, investments and savings. \\ 
    3. & Education & & & &\\
       &            & 3.1 &  Compulsory and \newline pre-school education & \thead{Education.CompulsoryAnd\\PreschoolEducation} & Compulsory education refers to the period of education that is required of all persons living in a country and is imposed by law. Pre-school education refers to formal childcare and education given prior to compulsory education. This topic covers data relating to pre-school, primary and lower secondary stages of education, regardless of whether the data focuses on students, teachers, subjects or skills taught, facilities etc.\\
       &            & 3.2 &  Education policy & Education.EducationalPolicy & 
      Discussions of policy and principles, and decisions made and principles adopted at national, regional or local level concerning education and its provision. Use note: For laws and regulations already implemented, use the topic 'Legislation and legal systems' as well.\\
       &            & 3.3 &  Higher and further \newline education & \thead{Education.HigherAndFurther\\Education} & Covers general education at ISCED levels 3-4 plus tertiary education, that is, upper secondary general education, and college, university of applied sciences, and university education. Includes data on students, teachers, subjects or skills taught, facilities etc.\\
       &            & 3.4 &  Life-long/continuing \newline education & \thead{Education.LifelongContinuing\\Education} & Refers to educational opportunities in varied forms provided for adults after they have left the formal education system. Adults may engage in such education to, for instance, improve their skills or qualifications, to retrain for a new line of work, or just to learn something new. Does not generally include education leading to a qualification, or employee training.\\
       \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    &            & 3.5 &  Vocational education training & \thead{Education.VocationalEducation \\ AndTraining} & Programmes that are designed for learners to acquire the knowledge, skills and competencies specific to a particular occupation, trade or class of occupations or trades. Vocational education may have work based components. Covers vocational education at ISCED levels 3-4 and apprenticeships. Includes data on students, teachers, subjects or skills taught, facilities etc. \\
    4. & Health & & & &\\
       &            & 4.1 &  Diet and nutrition & Health.DietAndNutrition & 
Nutritional processes, eating patterns and practices, and measurable nutritional parameters such as body mass index (BMI), weight, vitamin levels. \\
       &            & 4.2 &  Drug abuse, alcohol and smoking & \thead{Health.DrugAbuseAlcoholAnd\\Smoking} & Data on drug and other substance abuse. Data on smoking and drinking habits. Use note: For data covering medicinal use of recreational drugs (such as medicinal use of cannabis), use `Medication and treatment'.\\
       &            & 4.3 &  General health and well-being & Health.GeneralHealthAndWellbeing & Data on the general well-being or health status of an individual, group or population. May be objectively measured/observed or self-perceived. Well-being includes, for instance, physical and mental capacity or state, as well as social state.\\
       &            & 4.4 &  Health care services and policies & \thead{Health.HealthCareServicesAnd\\Policies} & Quality and availability of services, associated facilities and personnel within health care. Health care economy and policy decisions and principles at national, regional or local level regarding health care. Use note: For laws and regulations already implemented, use the topic 'Legislation and legal systems' as well. \\
          &            & 4.5 &  Medication and treatment & Health.MedicationAndTreatment& Treatment of disease, or procedure/s of preventing it. Patient care at individual level. Research on medication and treatment of a disease. Data on, for instance, surgical procedures, rehabilitation, doctor consultation, physical therapy, musculoskeletal manipulations, care in hospital or home, psychotherapy, investigative techniques, medication.\\
       &            & 4.6 &  Occupation health & Health.OccupationalHealth & Data on occupational exposures and diseases, occupational safety, sick leave, work ability and disability, or work-related disability pension. \\
        &            & 4.7 &  Physical fitness and exercise & Health.PhysicalFitnessAndExercise & 
       Data on people's general level of fitness, physical activity and exercise they take.\\
      &            & 4.8 &  Public health & Health.PublicHealth & 
       Prevention and control of disease and disability, and the promotion of physical and mental health of the population on the international,  \\
    \hline
    \end{tabularx}


\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
        &&&&& national, state, or municipal level. For instance, health promotion, disease prevention, impact of public health programmes, managing local, national or global health issues, epidemiology of a disease, condition, or pathogen, or disease outbreak. \\
        &            & 4.9 &  Reproductive health & Health.ReproductiveHealth & Reproductive process, function or system at any stage of life. Includes data on pregnancy, birth, family planning, contraception, abortion and menopause.\\
        &            & 4.10 & Signs and symptoms; pathological conditions & \thead{Health.SignsAndSymptoms\\PathologicalConditions} & Data on abnormal anatomical or physiological conditions, and objective or subjective manifestations of disease/symptoms, not classified as disease or syndrome (in which case 'Specific diseases, disorders or medical conditions' would be used). Includes clinical manifestations that can be objective when observed by a medical professional or subjective when perceived by the patient. E.g. pain, diarrhoea, rash, leg length inequality, insomnia, teeth grinding, inflammation, arrhythmia.\\
       &            & 4.11 & Specific diseases, disorders and medical conditions & \thead{Health.SpecificDiseases\\DisordersAndMedicalConditions} & Data on specific, diagnosed diseases, disorders or syndromes (often classified in ICD-10 or its earlier versions). For example, medical research on infectious diseases or the causes of diabetes, or data on the physical and mental recovery of people who have had heart surgery.\\
        &            & 4.12 & Wounds and injuries  & Health.WoundsAndInjuries & Wounds and injuries, both physical and psychological, caused either by accidents or violence (through individual or group aggressive behaviour). Use note: If work-related wounds or injuries, use 'Occupational health'.\\
    5. & History & & & History & 
In addition to this broader topic, use another topic for historical data. Example: for data on the working environments of family doctors in the 1960s, use HISTORY and 'Working conditions' plus 'Health care services and policies'. Use the HISTORY topic on its own only if a more specific topic cannot be found in this vocabulary. \\
    6. & \multicolumn{3}{l}{Housing and land use} & & \\
       &            & 6.1 & Housing  & HousingAndLandUse.Housing & Includes data measuring the standard of housing in a community, including social housing, as well as the availability and pricing of housing. Housing includes homes, second homes and holiday homes. \\
      &            & 6.2 & Land use and planning  & \thead{HousingAndLandUse.LandUse\\AndPlanning} & 
Includes both land use and land use planning. Land use planning refers to procedures carried out to ensure an optimal and sustainable use of land resources in rural and urban communities.\\
    \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    7. & \multicolumn{3}{l}{Labour and employment} & & \\
       &            & 7.1 & Employee training  & \thead{LabourAndEmployment.Employee\\Training} & 
    Internal corporate training and other employee training funded by the employer to increase employee skills and competence. Use note: Does not include apprenticeships, which are included in `Vocational education and training'.\\
        &            & 7.2 & Employment  & LabourAndEmployment.Employment & 
        Data on employment rate and statistics, labour market, job vacancies, job-seeking, job characteristics, employment of certain groups (e.g. youth or minority employment), employment services, career. Use note: For pay and remuneration use `Working conditions'. \\
       &            & 7.3 & Labour and employment policy  & \thead{LabourAndEmployment.LabourAnd\\EmploymentPolicy} & Data on employment policies relating to employment relations, the labour market and equality and discrimination at work; at national level policies include influencing the demand and supply of labour and the functioning of labour markets. Use note: For laws and regulations already implemented, use the topic `Legislation and legal systems' as well.\\
      &            & 7.4 & Labour relations/ conflict  & \thead{LabourAndEmployment.Labour\\RelationsConflict} & 
Relations between employers and employees.\\
       &            & 7.5 & Retirement  & LabourAndEmployment.Retirement & 
Includes all patterns of retirement such as phased or flexible retirement, data on retirement age and early retirement.\\
       &            & 7.6 & Unemployment  & \thead{LabourAndEmployment.\\Unemployment} & Data on unemployment rates and statistics, employment programmes and schemes, duration and frequency of unemployment, social and psychological impact of unemployment etc.\\
       &            & 7.7 & Working conditions  & \thead{LabourAndEmployment.Working\\Conditions} & 
The conditions under which employees work. For example, types of contract, working time (hours of work, rest periods, work schedules, overtime), pay and remuneration, physical aspects and mental demands of work, employee rights and responsibilities, workload, employee involvement in decision-making, leave entitlements, physical environment. Use note: For workplace safety issues, use also `Occupational health'.\\
    8. & \multicolumn{3}{l}{Law, crime and legal systems} & & \\
       &            & 8.1 & Crime and law enforcement & \thead{LawCrimeAndLegalSystems.Crime\\AndLawEnforcement} &
Data on crime, crime prevention, victims of crime, criminals, as well the police, secret service, correctional institutions (e.g. prisons, young people's correctional institutions), border control and customs. Also includes data on the staff and facilities of these agencies. \\
    \hline
    \end{tabularx}


\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    &            & 8.2 & Legislation and legal systems & \thead{LawCrimeAndLegalSystems.\\LegislationAndLegalSystems} & Data on international or national legislation, administrative regulations, judiciary system (powers and activities of courts), alternative dispute resolution and restorative justice, punishments. \\
    9. & \multicolumn{3}{l}{Media, communication and language} & & \\
       &            & 9.1 & Information society & \thead{MediaCommunicationAndLanguage.\\InformationSociety} & The creation, distribution, use, integration and manipulation of information as a significant economic, political, and cultural activity. For instance, data relating to e-commerce, e-government, social media, mobile devices, access to and use of the Internet, e-privacy, information and library resources. Use note: For data on the actual technologies, use `Information technology'. \\
       &            & 9.2 & Language and linguistics & \thead{MediaCommunicationAndLanguage.\\LanguageAndLinguistics} & Data from linguistic studies, linguistic analysis and sociolinguistics, as well as data on language policies, people's language skills, languages spoken at work and at home, attitudes towards minority languages etc.\\
       &            & 9.3 & Media & \thead{MediaCommunicationAndLanguage.\\Media} & 
Data referring to any type of mass media. For example, printed or online newspapers, magazines, television and the radio. Use note: Social media are indexed with `Information society'. \\
       &            & 9.4 & Public relations & \thead{MediaCommunicationAndLanguage.\\PublicRelations} &
 Measures adopted to enhance or preserve the image of individuals, companies, organisations, and governments for example by means of advertising, lobbying etc. \\
    10.& \multicolumn{3}{l}{Natural environment} & & \\  
       &            & 10.1 & Energy and natural resources & \thead{NaturalEnvironment.EnergyAnd\\NaturalResources} & 
Natural resources are assets such as land, forests, energy sources, water, minerals which exist naturally and can be used for economic production or consumption. Energy resources include fossil fuels such as oil, natural gas or coal, as well as nuclear, solar, tidal and wind or from living organisms that can be replaced. \\
       &            & 10.2 & Environment and conservation & \thead{NaturalEnvironment.Environment\\AndConservation} & 
Covers issues of environmental degradation, pollution, environmental protection, climate change, flood prevention, soil erosion. \\
       &            & 10.3 & Natural landscapes & \thead{NaturalEnvironment.Natural\\Landscapes} & Covers landscapes and elements of land that have not been directly changed by humans.\\
       &            & 10.4 & Plants and animals & \thead{NaturalEnvironment.PlantsAnd\\Animals} & 
Covers domesticated, production and wild animals, as well as all types of plants (e.g. flowers, trees, moss, vegetables)\\
    \hline
    \end{tabularx}


\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    11. & Politics & & &&\\
       &            & 11.1 &  Conflict, security and peace & Politics.ConflictSecurityAndPeace & Internal and international security and safety; internal and international conflicts; war and peace; national defence and defence forces (the army). Use note: The police are covered by `Crime and law enforcement'\\
     &            & 11.2 &  Elections & Politics.Elections & Data on elections, referendums, election campaigns, election results, candidates in elections, candidate selectors, election funding etc.\\
        &            & 11.3 & Government, political systems and organisations & \thead{Politics.GovernmentPolitical\\SystemsAndOrganisations} & Issues relating to national, regional and local government, governing bodies (e.g. the Government, Parliament, local government bodies), public administration, other political organisations such as political parties. For example, data on government policies, political parties and their policies, political party leaders, trust in government bodies.\\
       &            & 11.4 & International politics and organisations & \thead{Politics.InternationalPoliticsAnd\\Organisations} & Global governance, diplomacy, foreign policy, relations between countries, international organisations (e.g. the EU, WHO, UN, WTO), and international agreements.\\
       &            & 11.5 &  Political behaviour and attitudes & \thead{Politics.PoliticalBehaviourAnd\\Attitudes} & Data on party political attitudes, political engagement and participation in the political process, voting behaviour, satisfaction with government. Use note: For data on specific political doctrines, use `Political ideology'. \\
       &            & 11.6 &  Political ideology & Politics.PoliticalIdeology & Ideas, ideals and theories on the ways governments and societies can be organised. Major political ideologies include anarchism, democracy, liberalism, conservatism etc. \\
    12. & Psychology & & & & \\
    13.& \multicolumn{3}{l}{Science and technology} & & \\ 
       &            & 13.1 &  Biotechnology & ScienceAndTechnology.Biotechnology & Data referring to the use of biomolecular and cellular processes to create new products and technological processes.\\
       &            & 13.2 &  Information technology & \thead{ScienceAndTechnology.Information\\Technology} & 
       Information and communication technologies that are used in the home, workplace and other community setting. Use note: The use and impact of these technologies are covered by 'Information society'.\\
    14.& \multicolumn{3}{l}{Social stratification and groupings} & &  \\
       &            & 14.1 & Children  & \thead{SocialStratificationAndGroupings.\\Children} & Use note: May need an additional topic, if children are studied from a particular aspect.\\
       &            & 14.2 & Elderly  & \thead{SocialStratificationAndGroupings.\\Elderly} & Use note: May need an additional topic, if the elderly are studied from a particular aspect.\\
    \hline
    \end{tabularx}



\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}}  & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
       &            & 14.3 & Elites and leadership  & \thead{SocialStratificationAndGroupings.\\ElitesAndLeadership} & 
       Issues related to the existence, roles and impact of elites in society, that is, individuals or groups who have a large amount of power or influence over society, politics, wealth etc, either through decisions they make or, for example, through ideas or feelings that they express or represent. Includes issues related to influential people in all spheres of society, for example, decision-makers in political life, political party leaders, influential artists, prominent mass or social media figures etc.\\    
        &            & 14.4 & \thead{Equality, inequality and social\\ exclusion} & \thead{SocialStratificationAndGroupings.\\EqualityInequalityAndSocial\\Exclusion} & Issues relating to whether all individuals or groups of individuals have the same status and opportunities in society. Equality can be studied, for example, in terms of education, (financial) assets or income, occupational position, power, prestige, conditions of work and leisure time, access to services, and social relations. Marginalisation and social exclusion can be the result of systematic disadvantage in multiple areas of life, and people concerned may be deprived of rights, opportunities, resources and social integration. \\
       &&&&& Examples of data: statistics on income equality; perceived group-focused discrimination (e.g. towards foreigners, the homeless, asylum seekers); perceived differences between men and women regarding opportunities for leading roles in politics; impact of parental unemployment on children's education level and social networks.\\
       &            & 14.5 & Family life and marriage  & \thead{SocialStratificationAndGroupings.\\FamilyLifeAndMarriage} & Covers issues related to families, relatives, generations and household composition. For instance, data on child rearing, division of labour within the family, support provided for family members.\\
       &            & 14.6 & Gender and gender roles  & \thead{SocialStratificationAndGroupings.\\GenderAndGenderRoles} & Gender identity; gendered representation (e.g. representation of genders in decision-making bodies, in media, in literature etc); social, cultural and psychological traits linked to males and females; women's studies; men's studies; expected behaviour and choices according to gender roles and the impact of such expectations.
        \\
        &            & 14.7 & Minorities  & \thead{SocialStratificationAndGroupings.\\Minorities} & 
        Groups of individuals that differ from the majority of population in some way. Differentiating characteristics include, for instance, ethnicity, religion, health, sexual orientation, first language (mother tongue) and culture. Use note: For some minority issues, it may be useful to select additional topics such as `Equality, inequality and social exclusion' or `Language and linguistics'.\\
    \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}}  & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
     &            & 14.8 & Social and occupational mobility  & \thead{SocialStratificationAndGroupings.\\SocialAndOccupationalMobility} & Movement of individuals, families or groups of individuals in social and occupational status over time. The movement may be horizontal, that is, change in position within the range of same status, or vertical where individuals may move upwards or downwards in the status hierarchy. For example, labourers in declining industries may become labourers in some other industry (horizontal occupational mobility), or children in poor families may reach a higher social class than their parents (vertical inter-generational social mobility).\\
       &            & 14.9 & Youth  & \thead{SocialStratificationAndGroupings.\\Youth} & Use note: May need an additional topic, if young people are studied from a particular aspect.\\
    15.& \multicolumn{3}{l}{Social welfare policy and systems} & &  \\
       &            & 15.1 & Social welfare policy  & \thead{SocialWelfarePolicyAndSystems.\\SocialWelfarePolicy} & 
       Decisions made and principles adopted at national, regional or local level concerning social welfare, its funding and provision, for instance, who is entitled to what kind of social services and benefits and why, what is their level, and who can provide the services. For example, a policy that elderly people should remain in their homes for as long as possible, a policy relating to how long people can have an unemployment benefit. Use note: For laws and regulations already implemented, use the topic 'Legislation and legal systems' as well. \\
       &            & 15.2 & Social welfare systems/structures  & \thead{SocialWelfarePolicyAndSystems.\\SocialWelfareSystemsStructures} & 
       Issues related to the actual provision of social welfare, who provides social welfare services in practice and to what extent, how the actual services are structured. For example, questions on how a local government has organised services for the elderly. \\
        &            & 15.3 & Specific social services: Use and availability & \thead{SocialWelfarePolicyAndSystems.\\SpecificSocialServicesUseAnd\\Availability} & For example, data on the extent people use specific social services, opinions on the adequacy, accessibility and availability of specific services, and general satisfaction with them. For example, questions on what services elderly respondents have used, or use statistics on particular services.\\
    16.& \multicolumn{3}{l}{Society and culture} & &  \\
       &            & 16.1 & Community, urban and rural life  & \thead{SocietyAndCulture.Community\\UrbanAndRuralLife} & Data related to different aspects of life in the community, or in urban and rural areas. Opinions on and images of the neighbourhood, or of urban or rural areas. Services, facilities and business opportunities in the neighbourhood.\\
    \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}}  & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
        &            & 16.2 & Cultural activities and participation  & \thead{SocietyAndCulture.Cultural\\ActivitiesAndParticipation} & Active or passive participation in any kind of cultural activities, as well as opinions and perceptions of them. \\
       &            & 16.3 & Cultural and national identity & \thead{SocietyAndCulture.CulturalAnd\\NationalIdentity} & Data on identity formation, who people feel they are and where they feel they belong in terms of nationality, locality, social class, generation, ethnicity, religion or any other social/cultural grouping. Also covers exclusion of self or others from those groups. \\
       &            & 16.4 & Leisure, tourism and sport & \thead{SocietyAndCulture.LeisureTourism\\AndSport} & Recreation patterns, leisure time activities and hobbies. Includes sports spectatorship, competition sports, and travel for leisure. Use note: For data on exercise for keeping fit, use `Physical fitness and exercise'.\\
       &            & 16.5 & Religion and values & \thead{SocietyAndCulture.ReligionAnd\\Values} & 
       Data which addresses questions of religious behaviour, religious movements, spirituality, morality and other values.\\
       &            & 16.6 & Social behaviour and attitudes & \thead{SocietyAndCulture.SocialBehaviour\\AndAttitudes} & Data on social behaviour; social interaction and networks; social responsibilities; social norms and rules; and attitudes towards these issues. \\
       &            & 16.7 & Social change & SocietyAndCulture.SocialChange & Data on changes in the society, including attitudinal changes.\\
       &            & 16.8 & Social conditions and indicators & \thead{SocietyAndCulture.SocialConditions\\AndIndicators} & Covers all aspects of the quality of life and well-being of individuals and societies, as well as people's perceptions thereof. Use note: Depending on the aspect studied, `General health and well-being', `Equality, inequality and social exclusion' and `Economic conditions and indicators', etc. may be relevant as well.\\
        &            & 16.9 & Time use & SocietyAndCulture.TimeUse & Data on the amount of time spent by the population on various activities. \\
    17.& \multicolumn{3}{l}{Trade, industry and markets} & & \\
       &            & 17.1 & Agriculture and rural industry & \thead{TradeIndustryAndMarkets.Agricul-\\tureAndRuralIndustry} & Data on agricultural production and all rural industries which include, for example, fisheries and forestry. \\
       &            & 17.2 & Business/industrial management \newline and organisation & \thead{TradeIndustryAndMarkets.\\BusinessIndustrialManagement\\AndOrganisation} & Data on industry and business such as management, productivity, growth and decline, organisation structure, administration, investment in R\&D, markets and market share. \\
        &            & 17.3 & Foreign trade & \thead{TradeIndustryAndMarkets.Foreign\\Trade} & Exchange of capital, goods, or services across international borders.\\
    18.& \multicolumn{3}{l}{Transport and travel}  & TransportAndTravel &
       Includes all types of goods transport as well as commuting, public transport (trains, buses, underground etc), and urban transport networks. Data on mobility habits, for example, cross-border shopping, routes and \\
    \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{A. Topic Classification/Outcome Category (Cont.)}}}  & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    &&&&&  means used to access a location. Use note: For travel for leisure, use the topic `Leisure, tourism and sport'.\\
    19.& Other & & & Other & Use if the topic is known, but not found in the list.\\
    \hline\hline
    &&&&& \\
    \end{tabularx}
    
    
 \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{B. Study was designed to analyze (Source: New CV)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}} \\
    \hline\hline
    1. & \multicolumn{3}{l}{Heterogeneous treatment effects or effects by subgroup} & HeterogeneousTreatment & The study was designed to allow for the identification of heterogeneous treatment effects or effects by subgroup for one or more covariates.\\
    2. & \multicolumn{3}{l}{General equilibrium effects} & GeneralEquilibrium & The randomization was designed to be able to identify general equilibrium effects and the data contains the necessary information  (e.g., cluster randomization to measure cluster-level effects on prices, labor market outcomes, etc.).\\
    3. & \multicolumn{3}{l}{Spillovers or externalities} & SpilloversExternalities & The study was designed to measure spillover effects or externalities caused by the intervention (e.g., cluster randomization with varying saturation and data collected on everyone in the cluster).\\
    4. & \multicolumn{3}{l}{Interaction of different treatments} & TreatmentInteraction & The study’s interventions were assigned to arms in a way that allows the analysis of interaction effects (e.g., crossover designs). \\
    5. & \multicolumn{3}{l}{Varying treatment intensity} & VaryingTreatmentIntensity & The study was designed such that distinct arms were assigned different intensities of a broader intervention (e.g., a cash transfer that has \$20, \$40, and \$60 arms).\\
    6. & \multicolumn{3}{l}{Other} & Other & Any other noteworthy design or data features (e.g., data collected through new or innovative methods or data collected about a novel topic). \\
    \hline\hline
    &&&&& \\
    \end{tabularx}
 
 \newpage   
    \begin{tabularx}{\linewidth}{v a s m m b}
      \multicolumn{4}{l}{\textbf{\textsc{C. Study Sampling Method (Source: \href{https://ddialliance.org/Specification/DDI-CV/SamplingProcedure_1.1.html}{DDI})}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1.  & \underline{Total universe (population)} &  & & TotalUniverseCompleteEnumeration & All units (individuals, households, organizations, etc.) of a target population are included in the randomization. For example, if the target population is defined as the members of a trade union, all union members are invited to participate in the study. Also called ``census'' if the entire population of a regional unit (e.g. a country) is selected. \\
    2. & Probability & & & Probability & All units (individuals, households, organizations, etc.) of a target population have a non-zero probability of being included in the randomization sample and this probability can be accurately determined. Use this broader term if a more specific type of probability sampling is not known or is difficult to identify.\\
        && 2.1 & Simple random & Probability.SimpleRandom & All units of a target population have an equal probability of being included in the randomization sample. Typically, the entire population is listed in a ``sample frame'', and units are then chosen from this frame using a random selection method.\\
       & & 2.2 & Systematic random & Probability.SystematicRandom & A fixed selection interval is determined by dividing the population size by the desired sample size. A starting point is then randomly drawn from the sample frame, which normally covers the entire target population. From this starting point, units for the sample are chosen based on the selection interval. Also known as interval sampling.\\
       && 2.3 & Stratified & Probability.Stratified	& The target population is subdivided into separate and mutually exclusive segments (strata) that cover the entire population. Independent random samples are then drawn from each segment. For example, in a national public opinion survey the entire population is divided into two regional strata: East and West. After this, randomization units are drawn from within each region using simple or systematic random sampling. Use this broader term if the specific type of stratified sampling is not known or difficult to identify. \\
       & & 2.3.1 & Stratified: Proportional stratified & Probability.Stratified.Proportional & The target population is subdivided into separate and mutually exclusive segments (strata) that cover the entire population. Independent random samples are then drawn from each segment. Use this broader term if the specific type of stratified sampling is not known or difficult to identify. \\
        & & 2.3.2 & Stratified: Disproportional stratified & Probability.Stratified.Disproportional & The target population is subdivided into separate and mutually exclusive segments (strata) that cover the  entire population. In disproportional sampling the number of units chosen from each stratum is not proportional to the population size of the stratum when viewed against the  \\
    \hline
    \end{tabularx}
    
\newpage
     \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{C. Study Sampling Method (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
      &&&&&  entire population. The number of sampled randomization units from each stratum can be equal, optimal, or can reflect the purpose of the study, like oversampling of different subgroups of the population. \\
        && 2.4 & Cluster & Probability.Cluster	& The target population is divided into naturally occurring segments (clusters) and a probability sample of the clusters is selected. Data are then collected from all units within each selected cluster. Sampling is often clustered by geography, or time period. Use this broader term if a more specific type of cluster sampling is not known or is difficult to identify. \\
       & & 2.4.1 & Cluster: Simple random & Probability.Cluster.SimpleRandom & The target population is divided into naturally occurring segments (clusters) and a simple random sample of the clusters is selected. Data are then collected from all units within each selected cluster. For example, for a sample of students in a city, a number of schools would be chosen using the random selection method, and then all of the students from every sampled school would be included.\\
       & & 2.4.2 & Cluster: Stratified random & Probability.Cluster.StratifiedRandom & The target population is divided into naturally occurring segments (clusters); next, these are divided into mutually exclusive strata and a random sample of clusters is selected from each stratum. Data are then collected from all units within each selected cluster. For example, for a sample of students in a city, schools would be divided into two strata by school type (private vs. public); schools would be then randomly selected from each stratum, and all of the students from every sampled school would be included. \\
      & & 2.5 & Multistage & Probability.Multistage & Sampling is carried out in stages using smaller and smaller units at each stage, and all stages involve a probability selection. The type of probability sampling procedure may be different at each stage. For example, for a sample of students in a city, schools are randomly selected in the first stage. A random sample of classes within each selected school is drawn in the second stage. Students are then randomly selected from each of these classes in the third stage.\\
    3. & \multicolumn{3}{l}{Non-probability} & Nonprobability & The selection of randomization units (individuals, households, organizations, etc.) from the target population is not based on random selection. It is not possible to determine the probability of each element to be sampled. Use this broader term if the specific type of non-probability is not known, difficult to identify, or if multiple non-probability methods are being employed.\\   
          \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{C. Study Sampling Method (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
     & & 3.1 & Availability & Nonprobability.Availability & The sample selection is based on the units' accessibility/relative ease of access. They may be easy to approach, or may themselves choose to participate in the study (self-selection). Researchers may have particular target groups in mind but they do not control the sample selection mechanism.  Also called ``convenience'' or ``opportunity'' sampling.\\
     & & 3.2 & Purposive & Nonprobability.Purposive & Randomization units are specifically identified, selected and contacted for the information they can provide on the researched topic. Selection is based on different characteristics of the independent and/or dependent variables under study, and relies on the researchers' judgement. The study authors, or persons authorized by them have control over the sample selection mechanism and the universe is defined in terms of the selection criteria. Also called "judgement" sampling. Some types of purposive sampling are typical/deviant case, homogeneous/maximum variation, expert, or critical case sampling. \\
       & & 3.3 & Quota & Nonprobability.Quota & The target population is subdivided into separate and mutually exclusive segments according to some predefined quotation criteria. The distribution of the quotation criteria (gender/age/ethnicity ratio, or other characteristics, like religion, education, etc.) is intended to reflect the real structure of the target population or the structure of the desired study population. Non-probability samples are then drawn from each segment until a specific number of units has been reached. \\
     & & 3.4 & Respondent assisted & Nonprobability.RespondentAssisted & 	Randomization units are identified from a target population with the assistance of units already selected (adapted from ``Public Health Research Method'', ed. Greg Guest, Emily E. Namey, 2014). A typical case is snowball sampling, in which the researcher identifies a group of units that matches a particular criterion of eligibility. The latter are asked to recruit other members of the same population that fulfil the same criterion of eligibility (sampling of specific populations like migrants, etc.).\\
    4. & \underline{Mix of probability and non-probability sampling} & & & MixedProbabilityNonprobability & Sample design that combines probability and non-probability sampling within the same sampling process. Different types of sampling may be used at different stages of creating the randomization sample. For example, for a sample of minority students in a city, schools are randomly selected in the first stage. Then, a quota sample of students is selected within  \\
    \hline
    \end{tabularx} 
    
\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{C. Study Sampling Method (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    &&&&& each school in the second stage. If separate samples are drawn from the same target population using different sampling methods, the type of sampling procedure used for each sample should be classified separately. \\
    5. & Other &&& Other &\\
    \hline\hline
    &&&&& \\
    \end{tabularx}     
    
      \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{D. Unit of Obs./Randomization (Source: \href{https://ddialliance.org/Specification/DDI-CV/AnalysisUnit_1.0.0.html}{Adapted from DDI)}}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1. & Individual & & & Individual & Any individual person, irrespective of demographic characteristics, professional, social or legal status, or affiliation.\\
       &            & 1.1 & \underline{Political/social leader} & Individual.PoliticalSocialLeader &\\
       &            & 1.2 & \underline{Health providers} & Individual.HealthProvider & e.g. Doctors, nurses, midwives, etc.\\
       &            & 1.3 & \underline{Patient} & Individual.Patient &\\
       &            & 1.4 & \underline{Education providers} & Individual.EducationProvider & e.g. Teachers, principals, etc.\\
       &            & 1.5 & \underline{Student} & Individual.Student &\\
       &            & 1.6 & \underline{Farmer} & Individual.Farmer & \\
       &            & 1.7 & \underline{Employee} &Individual.Employee &\\
       &            & 1.8 & \underline{Business owner} & Individual.BusinessOwner&\\
       &            & 1.9 & \underline{Voter} & Individual.Voter &\\
   
       &            & 1.10 & \underline{Public servant} & Individual.PublicServant &\\
       &            & 1.11 & \underline{Parent} & Individual.Parent &\\
       &            & 1.12 & \underline{Other} & Individual.Other &\\
    2. & \multicolumn{3}{l}{\underline{Organization or legal entity}} & & Any kind of formal administrative and functional structure - includes associations, institutions, agencies, businesses, political parties, schools, etc.\\
       &            & 2.1 & \underline{Firm or business} & Organization.Firm &\\
       &            & 2.2 & \underline{Legal or administrative division of a} \newline \underline{firm or business} & Organization.DivisionOfFirm & e.g. Department  \\
       &            & 2.3 & \underline{Farm or agricultural business} & \thead{Organization.FarmOrAgricul-\\turalBusiness} &\\
    &            & 2.4 & \underline{School} & Organization.School & \\
           \hline
    \end{tabularx}

\newpage
     \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{D. Unit of Observation/Randomization (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
       &            & 2.5 & \underline{Legal or administrative division of} \newline \underline{a school}  & Organization.DivisionOfSchool  & e.g. subjects, cohorts, grades\\
       &            & 2.6 & \underline{University/college} & Organization.UniversityCollege \\
       &            & 2.7 & \underline{Legal or administrative division} \newline \underline{of a university/college} & \thead{Organization.DivisionOfUniver-\\sityCollege} & e.g. majors, cohorts \\
       &            & 2.8 & \underline{Hospital, health clinic or doctor's} \newline \underline{office} & Organization.HospitalClinicDoctorsOffice &\\
       &            & 2.9 & \underline{Other organization or legal entity} & Organization.Other &\\
    3. & \multicolumn{3}{l}{\underline{Family, household, or housing Unit}} &  & \\  
       &            & 3.1 & \underline{All individuals sharing certain} \newline \underline{amenities, resources, or facilities} &Household.IndividualsSharing &\\
       &            & 3.2 & \underline{Nuclear family} & Household.NuclearFamily & \\
       &            & 3.3 & \underline{Extended family} &Household.ExtendedFamily &\\
       &            & 3.4 & \underline{Parent(s) with dependent children} & Household.ParentsAndDependents &\\
       &            & 3.5 & \underline{Couples} & Household.Couples&\\
       &            & 3.6 & \underline{Shared accommodation or building} & Household.SharedBuilding&\\
       &            & 3.7 & Other &Household.Other &\\
    4. & Event/process & & & EventOrProcess & Any type of incident, occurrence, or activity. Events are usually one-time, individual occurrences, with a limited, or short duration. Examples: criminal offenses, riots, meetings, elections, sports competitions, terrorist attacks, natural disasters like floods, etc. Processes typically take place over time, and may include multiple "events" or gradual changes that ultimately lead, or are projected to lead, to a particular result. Examples: court trials, criminal investigations, political campaigns, medical treatments, education, athletes' training, etc.\\ 
    5. & \multicolumn{3}{l}{Geographic unit} & GeographicUnit & Any entity that can be spatially defined as a geographic area, with either natural (physical) or administrative boundaries. \\
       &            & 5.1 & \underline{Physical division of a firm or busi-} \newline \underline{ness}  & \thead{GeographicUnit.PhysicalDivision\\Firm} &  e.g. plants, production lines \\
       &            & 5.2 & \underline{Physical division of a school or} \newline \underline{ university/college} & \thead{GeographicUnit.PhysicalDivision\\School} & e.g. classrooms, buildings\\
         \hline
    \end{tabularx}


\newpage
\begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{D. Unit of Observation/Randomization (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}}  & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
       &            & 5.3 & \underline{Agricultural plot or physical unit} \newline \underline{  (stable, greenhouse)} &GeographicUnit.AgriculturalPlot & \\
       &            & 5.4 & \underline{Census tract, zip code, or other} \newline \underline{neighborhood-level administrative} \newline  \underline{unit based on geographic division}& \thead{GeographicUnit.CensusTractOr\\OtherNeighborhoodUnit} &\\
       &            & 5.5 & \underline{Village, community, or other} \newline \underline{town-level geographic division} & \thead{GeographicUnit.VillageOrOther\\TownLevelUnit}&\\
       &            & 5.6 & \underline{District, province, or other} \newline \underline{upper-level geographic division} & \thead{GeographicUnit.DistrictOrOther\\UpperLevelUnit} &\\
    6. & Time unit & & & TimeUnit & Any period of time: year, week, month, day, or bimonthly or quarterly periods, etc.\\    
    7. & Text unit & & & TextUnit & Books, articles, any written piece/entity.\\
    8. & \underline{Other group} & & & OtherGroup & Two or more individuals assembled together or having some unifying relationship.\\
    9. & Other & & & Other &\\
     \hline\hline
     &&&&& \\
    \end{tabularx}

        \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Source: New CV)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1. & \multicolumn{3}{l}{Agriculture} & Agriculture & & &\\
       &             & 1.1 & Technology and adoption & Agriculture.TechAdoption&\\
       &             & 1.1.1 & Technology and adoption: Irrigation & \thead{Agriculture.TechAdoption.Irriga\\tion} &\\
       &             & 1.1.2 & Technology and adoption: Improved seeds &Agriculture.TechAdoption.Seeds &\\
       &             & 1.1.3 & Technology and adoption: Sustainable farming & \thead{Agriculture.TechAdoption.Susta-\\ inableFarming} &\\
       &             & 1.2 & Agricultural productivity &Agriculture.Productivity &\\
       &             & 1.2.1 & Agricultural productivity: Fertilizer and agriculture inputs &Agriculture.Productivity.Inputs &\\
    \hline
    \end{tabularx}


\newpage
      \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
          &             & 1.2.2 & Agricultural productivity: Extension services & Agriculture.Productivity.Extension &\\
    2. & \multicolumn{3}{l}{Crime, violence, and conflict} &CrimeViolenceConflict &\\
       &             & 2.1 & Crime prevention &CrimeViolenceConflict.Prevention &\\
       &             & 2.1.1 & Crime prevention: Cognitive behavioral therapy &CrimeViolenceConflict.Prevention. \newline CognitiveTherapy &\\
       &             & 2.1.2 & Crime prevention: Re-entry \newline programming &CrimeViolenceConflict.Prevention. \newline ReentryProgramming & \\
       &             & 2.2 & Policing &CrimeViolenceConflict.Policing &\\

    3. & Education   &  & & &\\
       &             & 3.1 & Policy &Education.Policy & \\
       &             & 3.1.1 & Policy: Contract teachers &Education.Policy.ContractTeachers &\\ 
       &             & 3.1.2 & Policy: School meals &Education.Policy.SchoolMeals &\\

       &             & 3.1.3 & Policy: School choice & Education.Policy.SchoolChoice &\\
       
       &             & 3.1.4 & Policy: Scholarships & Education.Policy.Scholarships &\\
       &             & 3.1.5 & Policy: Curriculum/product & Education.Policy.Curriculum & \\
       &             & 3.2 & Practice & Education.Practice&\\
       &             & 3.2.1 & Practice: Tracking and remedial \newline education & \thead{Education.Practice.RemedialEduca-\\tion} &\\
        &             & 3.2.2 & Practice: Edutainment &Education.Practice.Edutainment & \\
       &             & 3.2.3 & Practice: Professional development & \thead{Education.Practice.ProfessionalDe-\\velopment} &\\
    4. & \multicolumn{3}{l}{Environment, energy, and climate change} & EnvironmentEnergyClimate & \\ 
       &             & 4.1 & Energy  & EnvironmentEnergyClimate.Energy &\\
       &             & 4.1.1 & Energy: Electrification  & \thead{EnvironmentEnergyClimate.Energy.\\Electrification} &\\
       &             & 4.1.1.1 & Energy: Electrification: Rural \newline electrification & \thead{EnvironmentEnergyClimate.Energy.\\Electrification.Rural}&\\
             \hline
    \end{tabularx}


\newpage
\begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
       &             & 4.1.1.2 & Energy: Electrification: Urban \newline electrification & \thead{EnvironmentEnergyClimate.Energy.\\Electrification.Urban} &\\
       &             & 4.1.2 & Energy: Renewable energy  & \thead{EnvironmentEnergyClimate.Energy.\\Renewable} &\\   
       &             & 4.1.3 & Transportation  & \thead{EnvironmentEnergyClimate.Trans-\\portation} &\\ 
       &             & 4.2 & Environment  & \thead{EnvironmentEnergyClimate.Environ-\\ment} &\\ 
       &             & 4.2.1 & Environment: Natural resource \newline management & \thead{EnvironmentEnergyClimate.Environ-\\ment.ResourceManagement} & \\ 
    5. & \multicolumn{3}{l}{Finance and financial inclusion} & Finance &\\  
        &             & 5.1 & Credit  & Finance.Credit& \\
        &             & 5.1.1 & Credit: Microfinance  & Finance.Credit.Microfinance & \\
        &             & 5.1.2 & Credit: Group lending  & Finance.Credit.GroupLending & \\
        &             & 5.2 & Insurance  & Finance.Insurance& \\
        &             & 5.3 & Global financial inclusion  &Finance.FinancialInclusion & \\
        &             & 5.4 & Financial literacy  & Finance.Literacy & \\
        &             & 5.5 & Savings  & Finance.Savings & \\
        &             & 5.5.1 & Savings: Commitment devices & Finance.Savings.CommitmentDevices& \\ 
    6. & Firms        & & & Firms & \\
        &             & 6.1 & Entrepreneurship/business skills & Firms.Entrepreneurship & \\
        &             & 6.1.1 & Entrepreneurship/business skills: \newline Business training &Firms.Entrepreneurship.Training & \\ 
        &             & 6.1.2 & Entrepreneurship/business skills: \newline Business skills & Firms.Entrepreneurship.BusinessSkills& \\ 

        &             & 6.1.3 & Entrepreneurship/business skills: \newline Business practice nudges/encoura- \newline gement & Firms.Entrepreneurship.PracticeNudges & \\ 
             \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}} \\
    \hline\hline
         &             & 6.1.4 & Entrepreneurship/business skills: \newline Business practice evaluation & \thead{Firms.Entrepreneurship.PracticeEva-\\luation} & \\  
        &             & 6.1.5 & Entrepreneurship/business skills: \newline Entrepreneurship & Firms.Entrepreneurship & \\
        &             & 6.2 & Recruitment and hiring & Firms.Recruitment& \\
        &             & 6.3 & Product advertising/campaigns &Firms.Advertising&  \\
        &             & 6.4 & Product pricing & Firms.Pricing& \\
    7.  & Gender        & & &Gender & \\   
        &             & 7.1 & Empowerment &Gender.Empowerment&  \\
        &             & 7.2 & Family planning &Gender.FamilyPlanning & \\
    8.  & Health        & & &Health& \\
        &             & 8.1 & Public health & Health.Public& \\
        &             & 8.1.1 &Public health: Non-communicable \newline diseases &Health.Public.NonCommunicable & \\
        & & 8.1.2 & Public health: Communicable \newline diseases & Health.Public.Communicable & \\
        &             & 8.1.2.1 &Public health: Communicable \newline diseases: Bed nets & \thead{Health.Public.Communicable.Bed\\Nets} & \\
        &             & 8.1.2.2 &Public health: Communicable \newline diseases: HIV & Health.Public.Communicable.HIV &  \\
        &             & 8.1.2.3 &Public health: Communicable \newline diseases: HIV: HIV/AIDS education & \thead{Health.Public.Communicable.HIV.\\Education} & \\
        &             & 8.1.2.4 &Public health: Communicable \newline diseases: Deworming & \thead{Health.Public.Communicable.Dewo-\\rming} & \\
        &             & 8.1.3 &Public health: Childhood development &Health.Public.ChildDevelopment &\\
        &             & 8.1.3.1 &Public health: Childhood development: Early childhood development & \thead{Health.Public.ChildDevelopment.\\EarlyChildhood} & \\
             \hline
    \end{tabularx}

\newpage
   \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
        &             & 8.1.3.2 &Public health: Childhood development: Teenagers & \thead{Health.Public.ChildDevelopment.\\Teenagers}&\\
        &             & 8.1.3.3 &Public health: Childhood development: Youth & Health.Public.ChildDevelopment.Youth &\\
        &             & 8.1.3.3.1 &Public health: Childhood development: Youth: Youth sports training & \thead{Health.Public.ChildDevelopment.Youth.\\SportsTraining} & \\
        &             & 8.1.4 &Public health: Nutrition &Health.Public.Nutrition& \\
        &             & 8.1.4.1 &Public health: Nutrition: Micronutrients &Health.Public.Nutrition.Micronutrients & \\
        &             & 8.1.5 &Public health: Reproductive health &Health.Public.Reproductive & \\
        &             & 8.1.6 &Public health: Health insurance & Health.Public.Insurance&\\
        &             & 8.1.6.1 &Public health: Health insurance: Microhealth insurance & \thead{Health.Public.Insurance.Microhealth\\Insurance} & \\
        &             & 8.1.7 &Public health: Health care delivery & Health.Public.CareDelivery&\\
        &             & 8.1.8 &Public health: Mental health & Health.Public.Mental&\\
        &             & 8.1.8.1 &Public health: Mental health: \newline Cognitive bias modification  & \thead{Health.Public.Mental.CognitiveBias\\Modification}& \\
        &             & 8.1.8.2 &Public health: Mental health: \newline Cognitive behavior therapy & \thead{Health.Public.Mental.CognitiveBeh-avior} &\\
        &             & 8.1.9 &Public health: Preventive health & Health.Public.Preventive&\\
        &             & 8.1.9.1 & Public health: Sanitation &Health.Public.Sanitation &\\
        &             & 8.1.9.1.1 &Public health: Sanitation: Water \newline treatment& \thead{Health.Public.Sanitation.WaterTre-\\atment} &\\
        &             & 8.1.9.1.2 &Public health: Sanitation: Safe \newline water storage&Health.Public.Sanitation.WaterStorage &\\
        &             & 8.2 & Individual health & Health.Individual &\\
        &             & 8.2.1 &Individual health: Drug (including placebo)&Health.Individual.Drug &\\
        &             & 8.2.2 &Individual Health: Device (including sham)&Health.Individual.Device &\\
             \hline
    \end{tabularx}   
        
\newpage
   \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline 
        &             & 8.2.3 &Individual health: Biological/ \newline vaccine& Health.Individual.Vaccine&\\
        &             & 8.2.4 & Individual health: Radiation & Health.Individual.Radiation&\\
        &             & 8.2.5 & Individual health: Behavioral & Health.Individual.Behavioral&\\
        &             & 8.2.6 & Individual health: Genetic &Health.Individual.Genetic &\\
        &             & 8.2.7 &Individual health: Dietary supplement &Health.Individual.Dietary &\\
        &             & 8.2.8 &Individual health: Combination \newline product & Health.Individual.Combination&\\
        &             & 8.2.9 & Individual health: Diagnostic test & Health.Individual.Diagnostic&\\
        &             & 8.2.10 &Individual health: Procedure/ \newline surgery &Health.Individual.Surgery &\\
    9.  & \multicolumn{3}{l}{Labor markets}  & LaborMarkets &\\
        &             & 9.1 & Migration & LaborMarkets.Migration &\\
        &             & 9.2 & Labor productivity &LaborMarkets.Productivity &\\
        &             & 9.3 & Training & LaborMarkets.Training&\\
        &             & 9.3.1 & Training: Coaching and mentoring & LaborMarkets.Training.Coaching& \\
        &             & 9.3.2 & Training: Soft skills &LaborMarkets.Training.SoftSkills &\\
        &             & 9.3.3 & Training: Job counseling & LaborMarkets.Training.JobCounseling&\\
        &             & 9.3.4 & Training: Apprenticeships and on-the-job training &LaborMarkets.Training.Apprenticeships & \\
    10. & \multicolumn{3}{l}{Peace and recovery} &PeaceAndRecovery & \\
    11. & \multicolumn{3}{l}{Political economy and governance} & PoliticalEconomyGovernance & \\
        &             & 11.1 & Elections & PoliticalEconomyGovernance.Elections & \\
        &             & 11.2 & Discrimination & \thead{PoliticalEconomyGovernance.Discrimi-\\nation} &  \\
        &             & 11.2.1 & Discrimination: Diversity quotas & \thead{PoliticalEconomyGovernance.Discrimi-\\nation.Quotas} & \\
        &             & 11.2.2 & Discrimination: Fake resumes/ \newline applications & \thead{PoliticalEconomyGovernance.Fake\\Resumes}&  \\
    \hline
    \end{tabularx}


\newpage
   \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline 
        &             & 11.3 & Corruption & \thead{PoliticalEconomyGovernance.Corru-\\ption}& \\ 
        &             & 11.3.1 & Corruption: Audits &\thead{PoliticalEconomyGovernance.Corru-\\ption.Audits} & \\
        &             & 11.4 & Social norms & \thead{PoliticalEconomyGovernance.Social\\Norms} & \\
        &             & 11.4.1 & Social norms: Beliefs & \thead{PoliticalEconomyGovernance.Social\\Norms.Beliefs}& \\
        &             & 11.4.2 & Social norms: Fairness & \thead{PoliticalEconomyGovernance.Social\\Norms.Fairness}& \\
        &             & 11.4.3 & Social norms: Norms change & \thead{PoliticalEconomyGovernance.Social\\Norms.NormsChange}& \\
        &             & 11.4.4 & Social norms: Charitable giving &  \thead{PoliticalEconomyGovernance.Social\\Norms.CharitableGiving}& \\
        &             & 11.5 & Government policy &PoliticalEconomyGovernance.Policy & \\
        &             & 11.5.1 & Government policy: Regulatory \newline information & \thead{PoliticalEconomyGovernance.Policy.\\RegulatoryInformation} &  \\
        &             & 11.5.2 & Government policy: Taxes &\thead{PoliticalEconomyGovernance.Policy.\\Taxes} & \\
        &             & 11.5.3 & Government policy: Subsidies & \thead{PoliticalEconomyGovernance.Policy.\\Subsidies} & \\
    12. & \multicolumn{3}{l}{Social protection/welfare} &SocialProtectionWelfare & \\ 
        &             & 12.1 & Cash transfers &SocialProtectionWelfare.CashTransfers & \\
        &             & 12.1.1 & Cash transfers: Conditional cash \newline transfers & \thead{SocialProtectionWelfare.CashTransfers.\\Conditional} & \\
        &             & 12.1.2 & Cash transfers: Unconditional cash \newline transfers & \thead{SocialProtectionWelfare.CashTransfers.\\Unconditional} &  \\
    \hline
    \end{tabularx}


\newpage
   \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{E. Intervention Type (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline    
        &             & 12.2 & Housing/neighborhoods & SocialProtectionWelfare.Housing & \\
        &             & 12.3 & Risk mitigation &SocialProtectionWelfare.RiskMitigation & \\
        &             & 12.4 & Consumption & SocialProtectionWelfare.Consumption & \\
        &             & 12.4.1 & Consumption: Targeting & \thead{SocialProtectionWelfare.Consumption.\\Targeting} & \\
        &             & 12.4.2 & Consumption: Consumer protection & \thead{SocialProtectionWelfare.Consumption.\\ConsumerProtection}& \\
        &             & 12.4.3 & Consumption: Improved stoves & \thead{SocialProtectionWelfare.Consumption.\\Stoves}&  \\
    13. & \multicolumn{3}{l}{Misc. Economic subject/topic} & MiscEconomic & \\ 
        &             & 13.1 & Behavioral economics & MiscEconomic.Behavioral &\\
        &             & 13.1.1 & Behavioral economics: Nudges and reminders &MiscEconomic.Behavioral.Nudges & \\       
        &             & 13.1.2 &Behavioral economics: Behavioral commitments & \thead{MiscEconomic.Behavioral.Commit-\\ments} & \\
        &             & 13.1.3 &Behavioral Economics: Time preferences & \thead{MiscEconomic.Behavioral.TimePrefe-\\rences} & \\
        &             & 13.2 & Information/networks & MiscEconomic.Behavioral.Networks & \\ 
        &             & 13.2.1 &Information/networks: Digital and mobile & \thead{MiscEconomic.Behavioral.Networks.\\Digital} & \\
        &             & 13.2.2 &Information/networks: Social networks & \thead{MiscEconomic.Behavioral.Networks.\\Social} & \\
        &             & 13.3 & Games &MiscEconomic.Games & \\
        &             & 13.4 & Incentives & MiscEconomic.Incentives & \\
        &             & 13.4.1 & Incentives: Monitoring & MiscEconomic.Incentives.Monitoring & \\
        &             & 13.4.2 & Incentives: Performance pay & \thead{MiscEconomic.Incentives.Performance\\Pay}& \\
    \hline\hline
    &&&&&\\
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{F. Intervention Assign. Strategy (Source: Adapted from \href{https://prsinfo.clinicaltrials.gov/definitions.html}{CT.gov)}}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}}& \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1. & \multicolumn{2}{l}{Parallel} && Parallel & Arms are assigned to one (or no) intervention in parallel for the duration of the intervention(s). \\
    2. & \multicolumn{2}{l}{Factorial} &&Factorial & Two or more interventions are partially or fully cross-randomized to arms and evaluated in parallel. \\
    3. & \multicolumn{2}{l}{Crossover} && Crossover & Arms are assigned to different interventions or combinations of interventions (including no intervention) during different phases of the study. \\
    4.  \multicolumn{2}{l}{\underline{Other}} && Other& Use free-text entry to describe the intervention assignment strategy used in the study. \\
    \hline\hline
    &&&&&\\

    \multicolumn{4}{l}{\textbf{\textsc{G. Kind of Data (Source: Adapted from DDI)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1. & \multicolumn{2}{l}{Sample survey data} & & SampleSurveyData & Survey data collected from a sample of an underlying population.  \\
    2. & \multicolumn{2}{l}{Census/enumeration data} && CensusData &   Data that covers a complete population.  \\
    3. & \multicolumn{2}{l}{Administrative records data} && AdministrativeData &    Information collected, used, and stored primarily for administrative (i.e., operational) rather than research purposes.\\
    4. & \multicolumn{2}{l}{Aggregate data} && AggregateData &   Data at a level of aggregation higher than the units represented in the study, such as country or state-level average household income. \\
    5.	& \multicolumn{2}{l}{Clinical data}  & & ClinicalData	&	Data either collected during the course of ongoing patient care or as part of a formal clinical trial program.		\\
    6. & \multicolumn{2}{l}{Event/transaction data} && EventData &  Data that describes an event or transaction, such as data recording sales/business transactions. \\
    7. & \multicolumn{2}{l}{Observation data/ratings} && ObservationData  &  Data collected as they occur (for example, observing behaviors, events, etc.), without attempting to manipulate any of the independent variables. \\
    8. & \multicolumn{2}{l}{Process-produced data} && ProcessProducedData &  Paradata or process metadata: Information about data cleaning and transformation processes.  \\
	    	   \hline
    \end{tabularx}

\newpage
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{G. Kind of Data (Source: Adapted from DDI)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    9. & \multicolumn{3}{l}{Time budgetdiaries} & TimeBudgetDiaries  & Data collected from respondent-produced diaries that contain information on their time use.\\
    10. & \multicolumn{3}{l}{\thead{\underline{Choice experiments for} \\ \underline{preference eliciation}}} & ChoiceExperiments & \\
         &           & 10.1 & Incentivized & ChoiceExperiments.Incentivized & Data produced from choice experiments with real-world incentives.\\
         &           & 10.2 & Hypothetical & ChoiceExperiments.Hypothetical & Data produced from hypothetical choice experiments (i.e., those that do not have any real-world implications for the respondents.) \\
    11. & \multicolumn{3}{l}{\thead{\underline{Economic games with} \\ \underline{participant interaction}}} & EconomicGames	& Laboratory or ``lab-in-the-field.'' Data collected from laboratory or lab-in-the-field games played by the respondents, such as dictator or trust games, with real-world incentives. \\
	12. & \multicolumn{3}{l}{Measurement and tests} &  MeasurementsAndTests &   \\
	    &       &   12.1	&	Educational & \thead{MeasurementsAndTests.Educati-\\onal} &	Assessment of knowledge, skills, aptitude, or educational achievement by means of specialized measures or tests. \underline{Includes standardized testing.}	\\
	    &      	&	12.2	&	Physical	&  MeasurementsAndTests.Physical &	Assessment of physical properties of living beings, objects, materials, or natural phenomena. For example, blood pressure, heart rate, body weight and height, as well as time, distance, mass, temperature, force, power, speed, GPS data on physical movement and other physical parameters or variables, like geospatial data.	\\
	    &       &	12.3	&	Psychological &	\thead{MeasurementsAndTests.Psycholo-\\gical} &	Assessment of personality traits or psychological/behavioral responses by means of specialized measures or tests. For example, objective tests like self-report measures with a restricted response format, or projective methods allowing free responses, including word association, sentence or story completion, vignettes, cartoon test, thematic apperception tests, role play, drawing tests, inkblot tests, choice ordering exercises, etc.	\\
    13.	& Textual data &&& TextualData	& Data taken or coded from texts, including but not limited to documents, reports, or speeches.\\
    14.	&	Other    &&& Other &	\\
    \hline\hline
    &&&&&\\
    \end{tabularx}

\newpage
%Time Method%
  \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{H. Time Method (Source: \href{https://ada.edu.au/wp-content/uploads/2018/03/ADA_Deposit_Form_v1-0.pdf}{Adapted from ADA})}}}  & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1. & \multicolumn{3}{l}{One-time cross-sectional data}  &&  \\
    2. & \multicolumn{3}{l}{Repeated cross-sectional data}  &&  \\
    3. & \underline{Panel} &&&& Datasets that contain baseline and endline surveys that track the same participants included here. \\
    4. & \multicolumn{3}{l}{\underline{N/A (Admin or similar)}}  &&  \\
    5. & Other &&&& \\
    \hline\hline
    &&&&&\\
    
    \multicolumn{4}{l}{\textbf{\textsc{I. Covariates: Individual (Source: \href{https://www.gesis.org/fileadmin/upload/SDMwiki/Hoffmeyer-Zlotnik_Standardisation_and_Harmonisation_of_Socio-Demographic_Variables.pdf}{Adapted from GESIS})}}}& \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}} \\
    \hline\hline
    1. & Sex            &   &   &Sex &  \\
    2. & Age            &   &   & Age &\\
    3. & Citizenship    &   &   & Citizenship & \\
    4. & \multicolumn{3}{l}{Marital status/registered partnership} &MaritalStatus &\\
    5. & Education      &   &   & Education &  \\
    6. & Labor status   &   &   & LaborStatus  & \\
       &                & 6.1   & Description of employment  &LaborStatus.EmploymentDescription & \\
       &                & 6.2   & Description of professional activity & LaborStatus.ProfessionalActivity & \\
       &                & 6.3   & Professional status &L aborStatus.ProfessionalStatus & \\
       &                & 6.4   & Attachment to the labor force &LaborStatus.LaborForceAttachment & \\
       &                & 6.5   & Previous employment  & LaborStatus.PreviousEmployment& \\
    7. & \multicolumn{3}{l}{Number of persons in the household} & NumberOfPersons & \\ 
   8. & Income          &   &   &Income &  \\
   9. & Other           &   &   &  Other & \\
   10. &  \multicolumn{3}{l}{N/A: No individual-level analysis} &NA& \\
    \hline\hline
    &&&&&\\
    \end{tabularx}

    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{J. Covariates: Higher (Source: New CV)}}}& \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1. & \multicolumn{3}{l}{Housing/property characteristics or amenities}  & HousingPropertyCharacteristics& \\ 
    2. & \multicolumn{3}{l}{\thead{Demographics of household members or household structure}}  &DemographicsHouseholdStructure& \\ 
    3. & \multicolumn{3}{l}{Household assets - ownership or debt}  &HouseholdAssets& \\ 
    4. & \multicolumn{3}{l}{Household income} &HouseholdIncome& \\ 
    5. & \multicolumn{3}{l}{Farm characteristics} &FarmCharacteristics& \\ 
    6. & \multicolumn{3}{l}{\thead{Demographic characteristics of town, village or other gover-\\nmental unit}} & TownLevelDemographics &\\ 
    7. & \multicolumn{3}{l}{\thead{Geographic characteristics of town, village or other govern-\\mental unit}} & GeographicCharacteristicsOfTown &\\ 
    8. & \multicolumn{3}{l}{\thead{Ethno-political characteristics of town, village, or other gov-\\ernmental unit}} & EthnopoliticalCharacteristicsOfTown & \\
    9. & \multicolumn{3}{l}{Crime, violence, or legal enforcement indicators} &CrimeAndLegalIndicators&\\ 
    10. & \multicolumn{3}{l}{Firm-level characteristics} &FirmLevelCharacteristics &\\ 
    11. & \multicolumn{3}{l}{School characteristics} & SchoolCharacteristics &\\ 
    12. & \multicolumn{3}{l}{Hospital or clinic characteristics}& HospitalOrClinicCharacteristics & \\ 
    13. & Other &&& \\
    \hline\hline
    &&&&&\\
    \end{tabularx}
    
    \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{K. Mode of Data Collection (Source: \href{https://ddialliance.org/Specification/DDI-CV/ModeOfCollection_2.0.html}{Adapted from DDI})}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    1.	&	Interview         	&		&		                    &	& A pre-planned communication between two (or more) people - the interviewer(s) and the interviewee(s) - in which information is obtained by the interviewer(s) from the interviewee(s). If group interaction is part of the method, use `Focus group'.	\\
    & & 1.1 &Face-to-face interview	 & Interview.FaceToFace	& Data collection method in which a live interviewer conducts a personal interview, presenting questions and entering the responses. Use this broader term if not CAPI or PAPI, or if not known whether CAPI/PAPI or not.\\
    \hline
    \end{tabularx}

\newpage
%Mode of Data Collection%
\begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{K. Mode of Data Collection (Source: \href{https://ddialliance.org/Specification/DDI-CV/ModeOfCollection_2.0.html}{Adapted from DDI})}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    	&	           	                &	1.1.1	&	Face-to-face: CAPI/CAMI	& Interview.FaceToFace.CAPICAMI	& Computer-assisted personal interviewing. Data collection method in which the interviewer reads questions to the respondents from the screen of a computer, laptop, or a mobile device like tablet or smartphone, and enters the answers in the same device. The administration of the interview is managed by a specifically designed program/application.	\\    
    	&		                        &	1.1.2	&	Face-to-face: PAPI	& Interview.FaceToFace.PAPI	&  Paper-and-pencil interviewing. The interviewer uses a traditional paper questionnaire to read the questions and enter the answers.	\\
    	&& 1.2 & Telephone interview	& Interview.Telephone & Interview administered on the telephone. Use this broader term if not CATI, or if not known whether CATI or not. \\
    	&		                        &	1.2.1	&	Telephone: CATI	& Interview.Telephone.CATI	& Computer-assisted telephone interviewing. The interviewer asks questions as directed by a computer, responses are keyed directly into the computer and the administration of the interview is managed by a specifically designed program.	\\
    	&		                        &	1.2.2	&	\underline{Telephone: PATI}	    & Interview.Telephone.PATI &	The interviewer uses a traditional paper questionnaire to read the questions and enter the answers; the survey is conducted through a telephone.	\\
    	&		                        &	1.3	&	Email	    & Interview.Email	& Interviews conducted via e-mail, usually consisting of several e-mail messages that allow the discussion to continue beyond the first set of questions and answers, or the first e-mail exchange.	\\
    	&		                        &	1.4	&	Web-based	    & Interview.WebBased	& An interview conducted via the Internet. Examples include interviews conducted within online forums or using web-based audio-visual technology enabling the interviewer(s) and interviewee(s) to communicate in real time.	\\
    	2. & \multicolumn{3}{l}{Self-administered questionnaire} &  SelfAdministeredQuestionnaire	& Self-administered questionnaire includes knowledge tests and preference elicitation.  \\

        &	           	                &	2.1	&	Paper	& SelfAdministeredQuestionnaire.Paper	& Self-administered survey using a traditional paper questionnaire delivered and/or collected by mail (postal services), by fax, or in person by either interviewer, or respondent.	\\
        &		                        &	2.2	&	Email	& SelfAdministeredQuestionnaire.Email	& Self-administered survey in which questions are presented to the respondent in the text body of an e-mail or as an attachment to an e-mail, but not as a link to a web-based questionnaire. Responses are also sent back via e-mail, in the e-mail body or as an attachment.	\\
        \hline
    \end{tabularx}

\newpage
   \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{K. Mode of Data Collection (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    	&		                        &	2.3	&	SMS/MMS	 & \thead{SelfAdministeredQuestionnaire.SMS\\orMMS}	& Self-administered survey in which the respondents receive the questions incorporated in SMS (text messages) or MMS (messages including multimedia content) and send their replies in the same format.	\\
    	&		                        &	2.4	&	Web-based	 & \thead{SelfAdministeredQuestionnaire.Web\\Based} &	Computer-assisted web interviewing (CAWI). Data are collected using a web questionnaire, produced with a program for creating web surveys. The program can customize the flow of the questionnaire based on the answers provided, and can allow for the questionnaire to contain pictures, audio and video clips, links to different web pages etc. (adapted from Wikipedia).	\\
    	&		                        &	2.5	&	CASI	    & \thead{SelfAdministeredQuestionnaire.Com-\\puterAssisted} &	Computer-assisted self-interview (CASI). Respondents enter the responses into a computer (desktop, laptop, Palm/PDA, tablet, etc.) by themselves. The administration of the questionnaire is managed by a specifically designed program/application but there is no real-time data transfer as in CAWI, the answers are stored on the device used for the interview. The questionnaire may be fixed form or interactive. Includes VCASI (Video computer-assisted self-interviewing), ACASI (Audio computer-assisted self-interviewing) and TACASI (Telephone audio computer-assisted self-interviewing).	\\
    	3. & \multicolumn{3}{l}{Self-administered writings and/or diaries} & SelfAdministeredWritingsAndDiaries & Narratives, stories, diaries, and written texts created by the research subject.\\
        &	           	                &	3.1	&	Email	& \thead{SelfAdministeredWritingsAndDiaries.\\Email}	&	Narratives, stories, diaries, and written texts submitted via e-mail messages. \\
    	&		                        &	3.2	&	Paper	& \thead{SelfAdministeredWritingsAndDiaries.\\Paper}	& Narratives, stories, diaries, and written texts created and collected in paper form.	\\
    	&		                        &	3.3	&	Web-based	& \thead{SelfAdministeredWritingsAndDiaries.\\WebBased}	 &	Narratives, stories, diaries, and written texts gathered from Internet sources, e.g. websites, blogs, discussion forums.	\\
    	4. & \multicolumn{3}{l}{Observation} & Observation & Research method that involves collecting data as they occur (for example, observing behaviors, events, etc.), without attempting to manipulate any of the independent variables. \\

    	 &  & 4.1 & Field observation	& Observation.Field & Observation that is conducted in a natural environment. Field observation is defined as interactions, not designed by the researcher. \\
    	     	    \hline
    \end{tabularx}
    
\newpage
\begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{K. Mode of Data Collection (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
        &	           	                &	4.1.1	&	Participant field observation	& Observation.Field.Participant &	Type of field observation in which the researcher interacts with the subjects and often plays a role in the social situation under observation. \underline{Note: ``Field observation'' is defined as interactions not designed by the}	\\
        &&&&& \underline{researcher.} \\
    	&		                        &	4.1.2	&	Non-participant	field observation & Observation.Field.Nonparticipant	& Observation that is conducted in a natural, non-controlled setting without any interaction between the researcher and his/her subjects.\\
          && 4.2 & Laboratory observation  & Observation.Laboratory	& Observation that is conducted in a controlled, artificially created setting. \underline{Note: ``Laboratory observation'' is defined as researcher-designed econo-} \\
         &&&&& \underline{mic games between participants}		\\
        &	           	 & 4.2.1   &	 \underline{Computer interactions: Participant}	& \thead{Observation.Laboratory.Computer.\\Participant}	& Computer-based economic games in which the researcher interacts with the subjects and often plays a role in the situation under observation. \\
    	&                & 4.2.2   &   \underline{Computer interactions:} \newline \underline{Non-participant} & \thead{Observation.Laboratory.Computer.\\Nonparticipant} & Computer-based economic games that are conducted without any interaction between the researcher and his/her subjects.\\
    	&                & 4.2.3   &   \underline{Computer interactions:} \newline \underline{Bot participant}  & \thead{Observation.Laboratory.Computer.\\BotParticipant} & Computer-based economic games in which a bot interacts with the subjects and often plays a role in the situation under observation \\
    	&                & 4.3.1   &   \underline{In-person interactions: Participant}  & Observation.Laboratory.Participant & Type of laboratory observation in which the researcher interacts with the subjects and often plays a role in the social situation under observation. Example: Observation of children's play in a laboratory playroom with the researcher taking part in the play. \\
    	&                & 4.3.2   &   \underline{In-Person interactions:Non-part-} \newline \underline{icipant} & \thead{Observation.Laboratory.Nonpart-\\icipant} &  Type of laboratory observation that is conducted without any interaction between the researcher and his/her subjects. \\
    6.	&	Recording	                    &		&	            	& Recording	& Registering by mechanical or electronic means, in a form that allows the information to be retrieved and/or reproduced. For example, images or sounds on disc or magnetic tape.	\\
    7. & \multicolumn{3}{l}{Content coding } & ContentCoding  &     As a mode of secondary data collection, content coding applies coding techniques to transform qualitative data (textual, video, audio or still-image) originally produced for other purposes into quantitative data (expressed in unit-by-variable matrices) in accordance with pre-defined categorization schemes. 	\\
            \hline
    \end{tabularx}
    \newpage
\begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{K. Mode of Data Collection (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}}\\
    \hline\hline
    8.	&	Aggregation	                    &		&	            	& Aggregation	& Statistics that relate to broad classes, groups, or categories. The data are averaged, totaled, or otherwise derived from individual-level data, and it is no longer possible to distinguish the characteristics of individuals within those classes, groups, or categories. For example, the number and age group of the unemployed in specific geographic regions, or national level statistics on the occurrence of specific offences, originally derived from the statistics of individual police districts.	\\

    9.	&	Other	                        &		&	            	& Other	& Use if the mode of data collection is known, but not found in the list.	\\
    10.	&	\underline{N/A}	                &		&	            	&	&	\\
    \hline\hline
    &&&&& \\

    \multicolumn{4}{l}{\textbf{\textsc{L. External Resources Types %(Source: \href{https://guide-for-data-archivists.readthedocs.io/en/latest/completeMetadata.html#good-practices-for-completing-the-external-resources-description}{Adapted from IHSN})
    }
    }
    } & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}} \\
    \hline\hline
    1.	&	\textit{Document}         	&		&		                    &	&	\\
    	&	           	                &	1.1	&	Administrative	& Document.Administrative	& This includes materials such as the survey budget; grant agreement with sponsors; list of staff and interviewers, etc.	\\
    	&		                        &	1.2	&	Analytical	&	Document.Analytical & This includes documents that present analytical output (academic papers, etc. This does not include the descriptive survey report.	\\
    	&		                        &	1.3	&	Questionnaire	& Document.Questionnaire	& This includes the actual questionnaire(s) used in the field.\\
    	&		                        &	1.4	&	Reference	    &Document.Reference	& Any reference documents that are not directly related to the specific dataset, but that provide background information regarding methodology, etc. For international standard surveys, this may for example include the generic guidelines provided by the survey sponsor.	\\
    	&		                        &	1.5	&	Report	    &	Document.Report & Survey reports, studies and other reports that use the data as the basis for their findings.	\\
    	&		                        &	1.6	&	Technical	    &Document.Technical	& Methodological documents related to survey design, interviewer’s and supervisor’s manuals, editing specifications, data entry operator’s manual, tabulation and analysis plan, etc.	\\
    	&		                        &	1.7	&	Other	        &Document.Other	& Miscellaneous items	\\
    2.	&	Audio	                    &		&	                    &Audio	&	Audio type files.	\\
    3.	&	Map	                        &		&	            	&Map	&	Any cartographic information. \\
    4.	&	Photo	                    &		&	            	&Photo	&	\\
                \hline
    \end{tabularx}
    
\newpage
%External Resources Types%
     \begin{tabularx}{\linewidth}{v a s m m b}
    \multicolumn{4}{l}{\textbf{\textsc{L. External Resources Types (Cont.)}}} & \multicolumn{1}{l}{\textbf{\textsc{Value}}} & \multicolumn{1}{l}{\textbf{\textsc{Notes}}} \\
    \hline\hline
    5.	&	Program	                    &		&	            	&Program	&	Programs generated during data entry and analysis (data entry, editing, tabulation and analysis). These can be zipped together (include a brief summary report to describe the contents)\\
    6.	&	Table	                    &		&	            	&Table	& Tabulations such as confidence intervals that may not be included in a general report.	\\

    7.	&	Video	                    &		&	            	&	Video & Video type files provided as additional visual information	\\
    8.	&	Website	                    &		&	            	&Website	& Link to related website(s), such as a link to a Redatam server, or to the website of the survey sponsor in the case of international survey programs like the DHS, LSMS, or MICS).	\\
    9. & \multicolumn{2}{l}{\underline{Database/Repository Entry}} & & DatabaseEntry& \\

    10.	&	\underline{PAP}	                        &		&	            	&PAP	&	\\
    11.	&	\underline{Codebook}               &		&	            	&Codebook	&	\\

    12. & \multicolumn{2}{l}{\underline{Related trial registry entry}}  & &RelatedTrialEntry & \\
    13. & \multicolumn{2}{l}{\underline{Related study/project}} && RelatedProject& \\
    14. & \multicolumn{2}{l}{\underline{Consent forms}}	& &ConsentForms&	\\
    15.	&	Other	                    &		&	            	&Other	&	\\
    \hline\hline
    \end{tabularx}
    
\end{landscape}
